Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-04-10 chap.tex
Added method summary

    \item $Dst$: A continuous hourly index which gives a measure of the weakening or strengthening of the Earth's equatorial magnetic field due to the weakening or strengthening of the ring currents and the geomagnetic storms \citep{DesslerAndParker}. 
\end{enumerate}

@@

\section{One Hour Ahead $Dst$: Model Design}

@@

>>>>

    \item $Dst$: A continuous hourly index which gives a measure of the weakening or strengthening of the Earth's equatorial magnetic field due to the weakening or strengthening of the ring currents and the geomagnetic storms \citep{DesslerAndParker}. A large negative value of $Dst$ ($ \leq -150 \ nT$) indicates occurence of geomagnetic storm events which are of particular importance in space weather prediction due to their effects on telecommunications infrastructure. 
\end{enumerate}

@@

\section{One Hour Ahead $Dst$: Model Design}\label{sec:modeldesign}

@@

\section{GP-AR and GP-ARX: Workflow Summary}

Section \ref{sec:modeldesign} brings together all the practical issues with respect to building of GP-AR and GP-ARX models for predicting $Dst$, they can be condensed to form the following steps.

\item \textbf{Data Preprocessing}: Three seperate data sets for model training and hyper-parameter selection, model order selection and model evaluation must be created. Care must be taken that the size of the training sets does not delay the processes of kernel hyper-parameter selection. The training, validation and test data sets created from this procedure must all contain non-overlapping geomagnetic storm events.

\item \textbf{Choice of model components}:  Kernel, mean function, model selection procedure.

\item \textbf{Model Order Selection}: In order to find appropriate values for the auto-regressive time lags $p, p_v, p_b$ for $Dst$, solar wind speed and IMF $B_z$ respectively, create models upto a certain maximum time lag i.e. $3 \leq p \leq 8$ for GP-AR and $3 \leq p + p_v + p_b \leq 8$ for GP-ARX. For each such model perform the model selection routine to select values of the kernel hyper-parameters and evaluate the resultant model on the validation set. Choose the value of $p, p_v, p_b$ which maximises predictive performance on the validation set.
